### 2023-10-10 chapters/paper_review/pretext.tex
Add hierarchical VAE section and update main contributions with research questions/hypotheses
Improve hyphenation and add "= for compound words
Updates to discussion

\begin{table}[h!]

@@

    self-supervised learning.]{

@@

    self-supervised learning. 

@@

\resizebox{0.98\textwidth}{!}{

@@

% \addtocounter{footnote}{1}
\footnotetext{\label{footnote:table:pretext}
$X=\{x_1,x_2,...,x_T\}$ is the input sequence in which $x_t$ can be an
acoustic feature vector (e.g., MFCC, filterbank, or spectrogram features)
or a waveform sample. 
$X_{[t_1:t_2]}$ represents $\{x_{t_1},x_{t_1+1},...,x_{t_2}\}$.
$X_{-[t_1:t_2]}$ represents $X$ in which the segment
$X_{[t_1:t_2]}=\{x_{t_1},x_{t_1+1},...,x_{t_2}\}$ is masked.
$x_{t}^{i}$ represents the $i$-th dimension of $x_t$.
If $x_t$ is a frame in a spectrogram, then the $i$-th dimension corresponds
to a specific frequency bin.
$X^{-[f,f+j]}$ refers to a spectrogram $X$ which is masked along the frequency
axis from the $f$-th to $(f+j)$-th bin. 
% $X_{-[t:t+k]}^{-[f,f+j]}$ refers to a spectrogram $X$ but masked along both time and frequency dimensions. 
% $X^*$ is a temporally permuted version of $X$, that is, the $x_t$ are randomly shuffled to form $X^*$. 
We indicate random temporal permutation of a sequence by indexing it with
the set $\mathcal{P}_t\triangleq\textsc{permute}([0,t])$, where
$\textsc{permute}(\cdot)$ returns a permutation of the given list. 
We indicate data augmentation (e.g., reverberation) by the function
$\textsc{augment}(\cdot)$. Subscripts indicate different augmentations. 
% $X^\prime$ is an augmented version of $X$ (e.g., $X$ with reverberation), while $X^{\prime\prime}$ is $X$ adding distortion different from  $X^\prime$.
$Z$ represents a localized latent representation sequence of $X$. %, and $Z^\prime$ and $Z^{\prime\prime}$ are the latent representation sequences of  $X^\prime$ and $X^{\prime\prime}$, respectively. 
% $Z$ represents a localized latent representation sequence and $Z^\prime$ is the latent representation sequence of $X^\prime$. 
$Z^{(l)}$ is $Z$ at the $l$-th layer of the model used to compute it.
$\bar{H}$ is the contextualized sequence $H$ obtained from an exponential
moving average (EMA) of the model undergoing training with no masking
applied.
$Q$ represents a sequence of quantized learned representations, and $C$ is
a sequence of discrete cluster IDs.
For contrastive models, we specify only positive targets.%
}

>>>>

\begin{table}

@@

    self"=supervised learning.]{

@@

    self"=supervised learning. 

@@

\resizebox{0.99\textwidth}{!}{

@@

% \addtocounter{footnote}{1}
\footnotetext{\label{footnote:table:pretext}
$X=\{x_1,x_2,...,x_T\}$ is the input sequence in which $x_t$ can be an
acoustic feature vector (e.g., MFCC, filterbank, or spectrogram features)
or a waveform sample. 
$X_{[t_1:t_2]}$ represents $\{x_{t_1},x_{t_1+1},...,x_{t_2}\}$.
$X_{-[t_1:t_2]}$ represents $X$ in which the segment
$X_{[t_1:t_2]}=\{x_{t_1},x_{t_1+1},...,x_{t_2}\}$ is masked.
$x_{t}^{i}$ represents the $i$-th dimension of $x_t$.
If $x_t$ is a frame in a spectrogram, then the $i$-th dimension corresponds
to a specific frequency bin.
$X^{-[f,f+j]}$ refers to a spectrogram $X$ which is masked along the frequency
axis from the $f$-th to $(f+j)$-th bin. 
% $X_{-[t:t+k]}^{-[f,f+j]}$ refers to a spectrogram $X$ but masked along both time and frequency dimensions. 
% $X^*$ is a temporally permuted version of $X$, that is, the $x_t$ are randomly shuffled to form $X^*$. 
We indicate random temporal permutation of a sequence by indexing it with
the set $\mathcal{P}_t\equiv\textsc{permute}([0,t])$, where
$\textsc{permute}(\cdot)$ returns a permutation of the given list. 
We indicate data augmentation (e.g., reverberation) by the function
$\textsc{augment}(\cdot)$. Subscripts indicate different augmentations. 
% $X^\prime$ is an augmented version of $X$ (e.g., $X$ with reverberation), while $X^{\prime\prime}$ is $X$ adding distortion different from  $X^\prime$.
$Z$ represents a localized latent representation sequence of $X$. %, and $Z^\prime$ and $Z^{\prime\prime}$ are the latent representation sequences of  $X^\prime$ and $X^{\prime\prime}$, respectively. 
% $Z$ represents a localized latent representation sequence and $Z^\prime$ is the latent representation sequence of $X^\prime$. 
$Z^{(l)}$ is $Z$ at the $l$-th layer of the model used to compute it.
$\bar{H}$ is the contextualized sequence $H$ obtained from an exponential
moving average (EMA) of the model undergoing training with no masking
applied.
$Q$ represents a sequence of quantized learned representations, and $C$ is
a sequence of discrete cluster IDs.
For contrastive models, we specify only positive targets.%
}
